PANCHANGE_data_preprocessing

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
Removed education cleaning from NBR demographics because these variables are in a different section for NBR.

# Specify cohort
```{r Specify cohort}
GLAD = TRUE
EDGI = FALSE
NBR = FALSE
RAMP = FALSE
```

@@

  nbr.dem.raw.id <- nbr.dem.raw %>%
    drop_na(subjectid) %>% # Drop NAs
    distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
    separate(ID.intm, into = "ID", sep = 7) %>%
    mutate(ID = as.numeric(ID),
           startDate.coping = startDate) %>% # Rename startDate
    select(
      Sample, # Sample
      ID, # ID
      startDate.coping, #Date when participant signed up to nbr
#      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
      Birthyear = demographics.year, # Birthyear
      Gender = demographics.which_gender_do_you_identify_with, # Gender
      Sex = demographics.select_questionnaire_items_medical, #Sex
      EduYrs = demographics.school_education_school_years.txt, # Years in education
      demographics.college_or_university_degree, # level of education - univeristy
      demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
      demographics.o_levelsgcses_or_equivalent, # level of education - gcse
      demographics.cses_or_equivalent, # level of education - cse
      demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
    ) %>%
    add_numeric(., exclude = exclude_cols_dem) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

>>>>

# Specify cohort
```{r Specify cohort}
GLAD = FALSE
EDGI = FALSE
NBR = TRUE
RAMP = FALSE
```

@@

  nbr.dem.raw.id <- nbr.dem.raw %>%
    drop_na(subjectid) %>% # Drop NAs
    distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
    separate(ID.intm, into = "ID", sep = 7) %>%
    mutate(ID = as.numeric(ID),
           startDate.coping = startDate) %>% # Rename startDate
    select(
      Sample, # Sample
      ID, # ID
      startDate.coping, #Date when participant signed up to nbr
#      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
      Birthyear = demographics.year, # Birthyear
      Gender = demographics.which_gender_do_you_identify_with, # Gender
      Sex = demographics.select_questionnaire_items_medical, #Sex
      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
    ) %>%
    add_numeric(., exclude = exclude_cols_dem) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
